%! Author = Sujal Singh
%! Date = 5/11/24

% Preamble
\documentclass[11pt]{ipu-ethics}

%\title{\textbf{ICT144: Assignment 1}}
%\author{Sujal Singh -- \{04119051723, IIOT--B1\}}

% Packages
\usepackage{amsmath}
\usepackage{tabularray}

% Document
\begin{document}
    \pagestyle{assignmentstart}
    \question{Attempt any four of the following questions:
        \begin{enumerate}[label=\alph*)]%
            \item Define value of time.
            \item Meaning of self-interest of an engineer.
            \item Define accountability.
            \item What is an autonomous computer?
        \end{enumerate}}

    \begin{enumerate}[label=1. \alph*)]
        \item{%
            The value of time is the idea that time is a scarce resource which requires careful management to achieve
            fruitful outcomes. In a second,
        }
    \end{enumerate}

    \newpage
    \pagestyle{fancy}

    \question{Need for commitment in the engineering profession.}

    \question{Explain Gillign's theory of moral development.}

    \question{What is relevant information? How is it used in social experiments?}

    \question{What are the factors that are affecting safety and risk?}

    \question{Differentiate the concepts of `Gift' and `Bribe'.}
    The following table describes the differences between a bribe and a gift\\~\\
    \begin{tblr}{colspec=|X[3]|X[2]|X[2]|,hlines}
        \textbf{Feature}                 & \textbf{Bribe}       & \textbf{Gift}            \\
        \textbf{Timing}                  & Before a decision    & After a decision         \\
        \textbf{Cost}                    & Large Amount         & Small amount             \\
        \textbf{Quality}                 & Poor                 & Good/High                \\
        \textbf{Giver's Relationship}    & Friend               & Not necessarily a friend \\
        \textbf{Transparency}            & Secret               & Open                     \\
        \textbf{Motive}                  & Undue favor expected & Favor or gratitude       \\
        \textbf{Consequence on Employer} & Damages reputation   & No damage                \\
    \end{tblr}

    \newpage

    \question{Mention some universally accepted ethical principles.}
\end{document}