\pagenumbering{gobble}
\pagestyle{empty}
\begin{center}
    \textbf{\huge Index} \\[20pt]
    \begin{longtblr}{colspec={|Q[m,c]|Q[12,m]|Q[3,c]|},hlines,vlines,
        cell{2-Z}{1} = {cmd=\textbf{\the\numexpr\arabic{rownum}-1}.},
        cell{1}{2}={c}}
        \textbf{No.} & \textbf{Question} & \textbf{Remarks} \\
        &%
        Write a program to perform string manipulation operations using set of pre-defined functions such as
        \texttt{find()}, \texttt{upper()}, \texttt{len()}, \texttt{max()} and \texttt{min()}, and fetch specific
        content from string.
        & \\
        &%
        Write a program to test and check the mathematical functions such as \texttt{ciel()}, \texttt{sqrt()},
        \texttt{pow()} and \texttt{factorial()}.
        & \\
        &%
        Write a program that receives a number as input from user and returns if it's an odd or even number.
        & \\
        &%
        Write a program that receives input from the user to calculate the area of a triangle.
        & \\
        &%
        Write a program that receives input from the user to calculate the area of a square.
        & \\
        &%
        Write a program that receive input from the user to calculate the area of rectangle.
        & \\
        &%
        Write a program to check if the input string is a palindrome or not.
        & \\
        &%
        Write a program that receives marks of a student for a subject as input and assigns a grade
        A$\|$B$\|$C$\|$D$\|$E$\|$F\@.
        & \\
        &%
        Write a program to compute the GCD of two numbers.
        & \\
        &%
        Write a program to check if the given number is an Armstrong number or not.\ Examples of Armstrong number
        are 153, 370, 371 etc.
        & \\
        &%
        Write a program to check if the input year is a leap year or not
        & \\
        &%
        Write a program to compute factorial of a given number.
        & \\
        &%
        Write a Program to generate Fibonacci series till 100.
        & \\
        &%
        Write a program to print a multiplication table of a given number.
        & \\
        &%
        Write a program to create two lists and perform the following operation's: add the elements of the two
        list, compare the contents of the two list, find the number of elements in the list, sort the elements of
        the list and reverse the contents of the list.
        & \\
        &%
        Write a Program to create and display the content of the tuple.\ Initialize the tuple with the name of the
        cities.\ Display content of the tuple along with name/index positions of the cities.
        & \\
        &%
        Write a program to create an array of even numbers till 14.\ Display the contents of array, compute the
        length of the array and also show how to delete a element from the desired position from the array.
        & \\
        &%
        Using \texttt{filter()} function, write a program to filter the elements which are greater than 9.
        & \\
        &%
        Using filter function, write a program to display multiple of 5 from a given array.
        & \\
        &%
        Write a program to create a file called ``input.txt'', perform write/read operation on it with a string
        ``Computer Science''.
        & \\
        &%
        Write a program to create a file called ``input.txt'', initialize it with a string of your choice and
        perform the read operation to read only the first 3 characters from the file.
        & \\
        &%
        Using NumPy, write a program to create 1-dimensional array, load it with numbers, and perform the
        operation of iteration and slicing on it.
        & \\
        &%
        Using NumPy, write a program to create multidimensional array, load it with the numbers and display the
        content of it.
        & \\
        &%
        Using NumPy, write a program to create two 1-dimensional array and perform the operation of iteration,
        sorting the contents of array and concatenating the contents of the array.
        & \\
        &%
        Using NumPy, initialize an array and display its dimensionality.
        & \\
        &%
        Using Pandas, create a dataframe, initialize it with the contents such as your enrollment Number and name
        and display them.
        & \\
        &%
        Create 2 arrays, using MatPlotLib, plot the graph with the content of the two arrays, with coordinates
        plotted on x-axis and y-axis.
        & \\
        &%
        Create a .csv file (with contents like age, weight and BMI). Read the content of the file and using
        Pandas and MatPlotLib, plot the graph.
        & \\
        &%
        Create a .csv file (with contents like age, weight and BMI). Read the content of the file and using
        Pandas and MatPlotLib, plot the histogram.
        & \\
        &%
        Write a program to create a class called ``Student'' with fields such as: Enrollment Number, USS Name,
        Branch Name, Student Name, etc.\ Instantiate a class and make a call to user defined function to display
        the details of students.
        & \\
        &%
        Define Employee Class with fields such as Employee ID and Employee Name.\ Instantiate the class, invoke
        the constructor and make a call to user defined function to display the information about employee.
        & \\
    \end{longtblr}
\end{center}